Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-19 providence/sections/prov.tex
added ballot manifest in one place

For any round $j\ge 2$, by Definition \ref{def:minervatwo}
and Lemma \ref{lemma:minerva2_kmin_exists},
$\mathcal{A}=\text{Correct}$ (the audit stops) if and only if
\begin{equation*}
\begin{aligned}
\omega_{j}(k_{j}, k_{j-1}, p_a, p_0, n_{j}, n_{j-1}, \alpha )\triangleq\\
\sigma(k_{j-1},p_a,p_0,n_{j-1})\cdot \tau_1(k_{j}-k_{j-1},p_a,p_0,n_j-n_{j-1})
\ge \frac{1}{\alpha}.
\end{aligned}
\end{equation*}
%Let $d_j=k_j-k_{j-1}$ be shorthand for the new draw.
%could do this for simpler notation^
By Lemma \ref{lemma:any_ratio_is_sigma_simple}
and Definition \ref{def:minerva_ratio}, this is equivalent to
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]}
$$$$\ge \frac{1}{\alpha}.
$$
By Lemma~\ref{lemma:minerva2_kmin_exists} and Definition~\ref{def:minervatwo},
we see that there exists a $k_{min, j} = k^{p_a, p_0, \alpha, k_{j-1}}_{min, j, n_{j-1}, n_j}  \leq k_j$ 
%$k_{min, j}\le k_j$ 
for which
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]}\ge
$$
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{min, j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{min, j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]} 
$$$$
\ge 
\frac{1}{\alpha}
$$
%Equivalently,
%$$
%\frac{Pr[K_{j} \ge k_{min, j}\wedge K_{j-1} = k_{j-1} \mid n_{j}^*, k_{j-2}^*, H_a]}{Pr[K_{j}\ge k_{min, j} \wedge K_{j-1} = k_{j-1} \mid n_{j}^*, k_{j-2}^*, H_0]}\ge \frac{1}{\alpha}.
%$$
%Taking the sum over all possible rounds and corresponding preceding values
%of $k$, we get
% Taking the sum over all possible audit histories, we get
The above may be rewritten as
\begin{equation*}
\begin{aligned}
\sum_{{k} = k_{min, j}}^{n_j} Pr[(K_{j} , K_{j-1}) = (k, k_{j-1}) \mid H_0, n_{j-1}, n_{j}] \leq \\
\alpha \sum_{{k} = k_{min, j}}^{n_j} Pr[(K_{j} , K_{j-1}) = (k, k_{j-1}) \mid H_a, n_{j-1}, n_{j}]
\end{aligned}
\end{equation*}
The left hand side above is the probability of stopping in the $j^{th}$ round and $K_{j-1} = k_{j-1}$, given the null hypothesis, which is smaller than $\alpha$ times the same probability given the alternate hypothesis. 
For different possible values of $k_{j-1}$, different round sizes $n_j$ can be used, and this same relationship will hold. 
That is, the relationship\footnote{\Minerva enforces a similar relationship between risk and stopping probability but does so at the level of the round rather than for each individual value of $K_{j-1}$. By enforcing this relationship for each value of $K_{j-1}$, \Providence is resistant to a strongly round-choosing adversary.} holds even if the values of $n_{j}$ depend on $k_{j-1}$, if $n_j$ is a function $n_j(\alpha, p_0, p_1, \bm{k_{j-1}}, \bm{n_{j-1}})$.

>>>>

For any round $j\ge 2$, by Definition \ref{def:minervatwo}
and Lemma \ref{lemma:minerva2_kmin_exists},
$\mathcal{A}=\text{Correct}$ (the audit stops) if and only if
\begin{equation*}
\begin{aligned}
\omega_{j}(k_{j}, k_{j-1}, p_a, p_0, n_{j}, n_{j-1}, \alpha )\triangleq\\
\sigma(k_{j-1},p_a,p_0,n_{j-1})\cdot \tau_1(k_{j}-k_{j-1},p_a,p_0,n_j-n_{j-1})
\ge \frac{1}{\alpha}.
\end{aligned}
\end{equation*}
%Let $d_j=k_j-k_{j-1}$ be shorthand for the new draw.
%could do this for simpler notation^
By Lemma \ref{lemma:any_ratio_is_sigma_simple}
and Definition \ref{def:minerva_ratio}, this is equivalent to
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]}
$$$$\ge \frac{1}{\alpha}.
$$
By Lemma~\ref{lemma:minerva2_kmin_exists} and Definition~\ref{def:minervatwo},
we see that there exists a $k_{min, j} = k^{p_a, p_0, \alpha, k_{j-1}}_{min, j, n_{j-1}, n_j}  \leq k_j$ 
%$k_{min, j}\le k_j$ 
for which
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]}\ge
$$
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{min, j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{min, j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]} 
$$$$
\ge 
\frac{1}{\alpha}
$$
%Equivalently,
%$$
%\frac{Pr[K_{j} \ge k_{min, j}\wedge K_{j-1} = k_{j-1} \mid n_{j}^*, k_{j-2}^*, H_a]}{Pr[K_{j}\ge k_{min, j} \wedge K_{j-1} = k_{j-1} \mid n_{j}^*, k_{j-2}^*, H_0]}\ge \frac{1}{\alpha}.
%$$
%Taking the sum over all possible rounds and corresponding preceding values
%of $k$, we get
% Taking the sum over all possible audit histories, we get
The above may be rewritten as
\begin{equation*}
\begin{aligned}
\sum_{{k} = k_{min, j}}^{n_j} Pr[(K_{j} , K_{j-1}) = (k, k_{j-1}) \mid H_0, n_{j-1}, n_{j}] \leq \\
\alpha \sum_{{k} = k_{min, j}}^{n_j} Pr[(K_{j} , K_{j-1}) = (k, k_{j-1}) \mid H_a, n_{j-1}, n_{j}]
\end{aligned}
\end{equation*}
The left hand side above is the probability of stopping in the $j^{th}$ round and $K_{j-1} = k_{j-1}$, given the null hypothesis, which is smaller than $\alpha$ times the same probability given the alternate hypothesis. 
For different possible values of $k_{j-1}$, different round sizes $n_j$ can be used, and this same relationship will hold. 
That is, the relationship\footnote{\Minerva enforces a similar relationship between risk and stopping probability but does so at the level of the round rather than for each individual value of $K_{j-1}$. By enforcing this relationship for each value of $K_{j-1}$, \Providence is resistant to a strongly round-choosing adversary.} holds even if the values of $n_{j}$ depend on $k_{j-1}$, if $n_j$ is a function $n_j(\alpha, p_0, p_1, ballot\_manifest, \bm{k_{j-1}}, \bm{n_{j-1}})$.
